Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
clean the summary

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level. The bound-proton BSA is largely suppressed compared to 
the free proton BSA. This surprising result opens a new avenue for progress in 
the understanding quarks and gluons in the nuclear medium.

>>>>

%conclusion
In summary, we have presented the first BSA measurment associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results were compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
surprising result opens a new avenue for progress in the understanding quarks 
and gluons in the nuclear medium.
